---
title: "ggplot2vis"
author: "Tanvir"
date: "`r Sys.time()`"
output: 
    html_document:
      toc: true
      toc_float: 
       collapsed: false

---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

Loading required packages

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)
library(ggthemes)
library(ggThemeAssist)
library(data.table)
```

Setting Global Theme

```{r}
theme_set(theme_classic())
```

# Data

```{r}
student <- fread("Result/Cleaned_student_data.csv")
```

This dataset contains `r nrow(student)` students.

# Scatter Plot

```{r}
ggplot(student, aes(x = Math_score, y = Reading_score, size = Writing_score)) + geom_point(aes(colour = Gender)) + labs(title = "Scatter plot of Math and Reading score", x = "Math Score", y = "Reading Score") + scale_fill_manual(values = c("female" = "#6C1C80", "male"= "#123B96"))
```

Females comparatively scored better score than males. 

# Histogram

```{r}
ggplot(student) + geom_histogram(aes(x = Math_score, fill = Gender), bins = 10, col = "#ffffff", alpha = 0.6) + coord_cartesian(expand = FALSE)

```

## Facetwrap with ggthemes

```{r}
ggplot(student) + geom_histogram(aes(x = Math_score, fill = Gender), bins = 10, col = "#ffffff", alpha = 0.6) + facet_wrap(vars(Gender), ncol = 1) + theme_pander()
```

## Facetgrid with themebw

```{r}
ggplot(student) + geom_histogram(aes(x = Math_score, fill = Gender), bins = 10, col = "#ffffff", alpha = 0.6) + facet_grid(rows = vars(Gender), cols= vars(Test_prep_course)) + theme_bw()
```

# Plot customization using theme()

```{r}
ggplot(student,
       aes(x = Math_score, y = Reading_score, size = Writing_score)) + geom_point(aes(colour = Gender)) + labs(title = "Scatter plot of Math and Reading score", x = "Math Score", y = "Reading Score") + scale_fill_manual(values = c("female" = "#6C1C80", "male" = "#123B96")) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", size = 16),
    axis.title.x = element_text(face = "italic", size = 12),
    axis.title.y = element_text(face = "italic", size = 12),
    plot.background = element_rect( fill = "grey90")
  ) + guides(size = "none")
```


# Color on histogram

```{r}
ggplot(student) + geom_histogram(aes(x = Math_score, fill = Gender), bins = 10, col = "#ffffff", alpha = 0.6) + facet_wrap(vars(Gender), ncol = 1) + theme_pander() + scale_fill_manual(values = c("female" = "#6C1C80", "male"= "#123B96"))


p1 <- ggplot(student) + geom_histogram(aes(x = Math_score, fill = Gender), bins = 10, col = "#ffffff", alpha = 0.8) + facet_wrap(vars(Gender), ncol = 1)+ scale_fill_brewer(palette = "Set2")
```

# Plotly

```{r}
p1 %>% plotly::ggplotly()

p2 <- ggplot(student, aes(x = Grade, y = Math_score)) + geom_boxplot() +
  geom_jitter()
plotly::ggplotly(p2)
```

The highest math scores are obtained by grade A scorer students.